---
output: github_document
always_allow_html: yes
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Rmatch

<!-- badges: start -->
<!-- badges: end -->

Rmatch is a package that aims to assist you in any matching task that involves two datasets and (approximate) string matching

## Installation

You can install the development version of Rmatch like so:

``` r
# devtools::install_github("https://github.com/MatthiasUckert/Rmatch")
```

## Example (Step-by-Step)

Basic usage using build-in datasets. Check out the vignette for full specification

```{r example}
library(Rmatch); library(kableExtra); library(tidyverse)
```

Match Data:
You need 2 datasets, a source table (data you want to match) and a target table (data you want to match against).

```{r}
tab_source <- table_source
tab_target <- table_target
```

First, make sure your datasets are correcly formatted.
```{r}
check_data(tab_source, tab_target)
```

Standardizing columns won't harm
```{r}
cols_match <- c("name", "iso3", "city", "address")
tab_source <- standardize_data(tab_source, cols_match)
tab_target <- standardize_data(tab_target, cols_match)
```

Check again
```{r}
check_data(tab_source, tab_target)
```


Let's match the two dataframes
```{r}
cols_join <- c("name", "iso3")
cols_exact <- "iso3"
method <- "soundex"
tab_match <- match_data(
  .source = tab_source,
  .target = tab_target,
  .cols_match = cols_match,
  .cols_join = c("name", "iso3"),
  .cols_exact = cols_exact,
  .method = method,
)
```


```{r echo=FALSE}
tab_match %>%
  head() %>%
  kbl(align = "c") %>%
  kable_paper()%>%
  kable_styling(
    bootstrap_options = "condensed", 
    html_font = "Times New Roman", 
    font_size = 12
    )
```

Let's calculate the best matches
```{r}
tab_score <- scores_data(
  .matches = tab_match,
  .source = tab_source,
  .target = tab_target,
  .cols_match = cols_match,
  .cols_exact = cols_exact
  )
```

```{r echo=FALSE}
tab_score %>%
  head() %>%
  kbl(align = "c") %>%
  kable_paper()%>%
  kable_styling(
    bootstrap_options = "condensed", 
    html_font = "Times New Roman", 
    font_size = 12
    )
```

Finally Deduplicate Matches, DONE(ish)
```{r}
col_score <- "sms"
tab_final1 <- dedup_data(
  .score = tab_score,
  .source = tab_source,
  .target = tab_target,
  .cols_match = cols_match,
  .col_score = col_score
)
```

```{r echo=FALSE}
tab_final1 %>%
  head() %>%
  kbl(align = "c") %>%
  kable_paper()%>%
  kable_styling(
    bootstrap_options = "condensed", 
    html_font = "Times New Roman", 
    font_size = 10
    )
```

## Example (All-in-One)
```{r}
tab_final2 <- match_complete(
  .source = table_source,
  .target = table_target,
  .cols_match = cols_match,
  .cols_join = cols_join,
  .cols_exact = cols_exact,
  .method = method,
  .standardize = TRUE,
  .col_score = col_score
)
```
```{r}
all.equal(tab_final1, tab_final2)
```


```{r echo=FALSE}
tab_final2 %>%
  head() %>%
  kbl(align = "c") %>%
  kable_paper()%>%
  kable_styling(
    bootstrap_options = "condensed", 
    html_font = "Times New Roman", 
    font_size = 10
    )
```

## Code of Conduct

Please note that the Rmatch project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
