---
output: github_document
always_allow_html: yes
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Rmatch

<!-- badges: start -->
<!-- badges: end -->

Rmatch is a package that aims to assist you in any matching task that involves two datasets and (approximate) string matching

## Installation

You can install the development version of Rmatch like so:

``` r
# devtools::install_github("https://github.com/MatthiasUckert/Rmatch)
```

## Example

Basic usage using build-in datasets. Check out the vignette for full specification

```{r example}
library(Rmatch); library(kableExtra)
```

Match Data:
You need 2 datasets, a source table (data you want to match) and a target table (data you want to match against).

```{r}
tab_source <- table_source
tab_target <- table_target
```

First, make sure your datasets are correcly formatted.
```{r}
check_data(tab_source, tab_target)
```

Standardizing columns won't harm
```{r}
cols <- c("name", "iso3", "city", "address")
tab_source <- standardize_data(tab_source, cols)
tab_target <- standardize_data(tab_target, cols)
```

Check again
```{r}
check_data(tab_source, tab_target)
```


Let's match the two dataframes
```{r}
tab_match <- match_data(
  .source = tab_source,
  .target = tab_target,
  .cols = c("name", "iso3", "city", "address"),
  .min_sim = .2,
  .progress = FALSE
)
```


```{r echo=FALSE}
tab_match %>%
  head() %>%
  kbl() %>%
  kable_paper() %>%
  kable_styling(bootstrap_options = "condensed", html_font = "Times New Roman", font_size = 12)
```

Let's calculate the best matches
```{r}
tab_score <- scores_data(tab_match)
```

```{r echo=FALSE}
tab_score %>%
  head() %>%
  kbl() %>%
  kable_paper()%>%
  kable_styling(bootstrap_options = "condensed", html_font = "Times New Roman", font_size = 12)
```

Finally Deduplicate Matches, DONE(ish)
```{r}
tab_final <- dedup_data(
  .score = tab_score,
  .source = tab_source,
  .target = tab_target,
  .col = "score_square"
)
```

```{r echo=FALSE}
tab_final %>%
  head() %>%
  kbl() %>%
  kable_paper() %>%
  kable_styling(bootstrap_options = "condensed", html_font = "Times New Roman", font_size = 8)
```


## Code of Conduct

Please note that the Rmatch project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
